\chapter{Development Methodologies}

In order to ensure all objectives and goals that have been set within this 
project are completed to the highest quality and upon time, a software 
development methodology will need to be chosen. Dividing a larger project into 
a set number of defined processes may seem like additional unnecessary work, 
but the advantages of this process far outweigh the disadvantages 
\citep{knott_dawson99}.

The defined processes combine together to form part of a process model. The 
process model will allow for the following achievements \citep{knott_dawson99}:

\begin{itemize}
  \item Adding an element of control and planning
  \item Allowing for progress to be mapped visually
  \item Providing a structured approach to development
  \item Allowing for a higher quality of code and documentation to be produced
\end{itemize}

The Systems Development Life Cycle (SDLC) was one of the first formalised 
methodologies for building software. The SDLC utilises a methodical and 
structured approach to analysing, designing, building and testing software, to 
which many methodologies follow this rigid structure \citep{elliott04}. 


% Waterfall overview 
\newpage
\input{development_methodologies/waterfall.tex}


% Spiral overview 
\newpage
\input{development_methodologies/spiral.tex}


% Agile overview 
\newpage
\input{development_methodologies/agile.tex}


% Rapid Application Development overview 
\newpage
\input{development_methodologies/rad.tex}


% Final chapter summary
\section{Summary}
In order to achieve the best possible product, it is clearly evident that the 
project should be developed utilising a feature driven approach. This will 
allow for any revisions, modifications, and changes to be considered and 
implemented with as little delay as possible, as well as little impact upon the
rest of the project.

The projects requirements are not set directly by an external client, and hence
it is possible for the requirements to be changed. It is because of these 
uncertainties that an agile development methodology would be best adopted by 
this project.

This methodology will not only allow for the requirements to change, but can 
allow for substantial research to be able to take place upon new topic areas if
needed. Agile development methodologies allow for multiple releases of 
software, which fundamentally means that the team is able to use prototyping 
techniques to find the best outcome to a given problem.
