\newpage
\section{Mandated Constraints}

The following section describes the constraints that effect the design of the
product. The product that is to be developed cannot be successful unless these
constraints have been accomplished.

%Solution Constraints
\subsection{Solution Constraints}

\noindent\llap{\textbf{[R1/1]}}The product shall be built for the following platforms:\\
\begin{enumerate}
		\item Blackberry
		\item iOS 
		\item Android
\end{enumerate}

\textbf{Rationale:}  The product it to be able to be used on the go.\\
\textbf{Volatility:} High


\noindent\llap{\textbf{[R2/1]}}The product shall require an Internet connection. \\

\textbf{Rationale:}  The product cannot work without an Internet connection.\\
\textbf{Volatility:} High

%Implementation Environment of the System
\subsection{Implementation Environment of the System}

\noindent\llap{\textbf{[R3/1]}}The product shall run on the following operating systems:\\

\begin{enumerate}
		\item Blackberry 10.2
		\item iOS 7
		\item Android 4.2 Jellybean
\end{enumerate}

\textbf{Rationale:}  The product is new therefore run on the latest software\\
\textbf{Volatility:} High

%Partner or Collaborative Applications
\subsection{Partner or Collaborative Applications}

\noindent\llap{\textbf{[R4/1]}}The product shall allow the user to login with their facebook account.

\textbf{Rationale:}  The product will allow a user to login in order to keep a search history, instead of creating a new authentication the user should be able to login using third part applications\\
\textbf{Volatility:} Low

%Off-the-Shelf Software
\subsection{Off-the-Shelf Software}

\noindent\llap{\textbf{[R5/1]}}The product shall make use of the Apache OpenNLP Library.

\textbf{Rationale:}  In order for the product to recognize the clues the best possible technique is to use Natural Language processing tools.\\
\textbf{Volatility:} Medium

%Schedule Constraints
\subsection{Schedule Constraints}

\noindent\llap{\textbf{[R6/1]}}The product shall be completed on or before the 18th April 2014.

\textbf{Rationale:}  The final deadline for all deliverables are 18/04/2014. \\
\textbf{Volatility:} High

%Budget Constraints
\subsection{Budget Constraints}

\noindent\llap{\textbf{[R7/1]}}The product shall be developed using all freely available tools and the only constraint of budget shall be the time the project resources put into to the product.

\textbf{Rationale:}  As the resources of the project are students, the product needs to be developed using the least amount of money as possible. The necessary steps should be taken to ensure that no costs are accumulated while developing the product \\
\textbf{Volatility:} Medium

