%%%
%% Problem Analysis :: Research Areas
%%%
\section{Research Areas}

Before undertaking the project an initial review was conducted. The review's 
objective was to determine the feasibility of the project as a whole. The 
review also covered whether or not the project has been completed before.

From the outlined background and problem information it is clear that cryptic 
crosswords are a popular form of entertainment. It is also clear that some 
clues are particularly difficult to solve, and users may often ask other people
for help in solving a given clue.


%%%
%% Problem Analysis :: Research Areas :: Cryptic Crosswords
%%%
\subsection{Cryptic Crosswords}

A review of the national UK newspapers was conducted to determine whether or 
not there is a pattern in cryptic crosswords. Of all the newspaper's websites 
that were reviewed (The Guardian, The Times, The Independent and The Mirror) it 
was clear that all cryptic crosswords are of the same style.

Each clue is categorised as being either `across' or `down' with its 
corresponding grid number, as well as containing the number of letters the 
answer should be. An example is shown below:

\begin{quote}
12. The seamstress's sensation? (4, 3, 7) =\textgreater  PINS AND NEEDLES
\end{quote}

The Guardian's website utilises web standard technologies such as HTML and CSS, 
and also provides an option to solve a clue. The Mirror's website follows a 
similar approach to the Guardian's website; however solutions can only be 
obtained by dialing a premium telephone number.

The Times and the Independent both utilise a different approach and that is to 
serve a Java applet. Both Java applets allow the user to solve a clue should 
they get stuck. The Times provides puzzles as part of their paid subscription 
service.

All of the above newspapers publish cryptic crosswords upon a daily basis, with
the solutions to the crosswords appearing in the next day's newspaper.

Following from the crossword review, a second review into cryptic crossword 
solvers was undertaken. The objective of this review was to determine whether 
or not computerised cryptic crossword solvers exist. The three cryptic 
crossword solvers that were identified were One Across, Crossword Tools and 
Cryptic Solver.

Each of the solvers manages to solve some clues with the same answers, with 
other clues providing a range of possible answers.

Crossword Tools \citep{crosswordtools} is a paid subscription based service, 
which allows users to enter a clue and a pattern. A pattern can contain part of
the answer or the number of letters the answer has. If multiple answers are 
available, they are displayed. An example is shown below:

\begin{quote}
Kind of dog (10) =\textgreater the answer is 10 letters long.

Kind of dog (?????????r) =\textgreater the answer is 10 letters long, final 
letter is `r'.
\end{quote}

Cryptic Solver \citep{crypticsolver} is a free service that offers the same 
functionality as Crossword Tools. Although Cryptic Solver does provide the 
correct answer, it does not necessarily provide the correct answer at the top 
of the list.

Finally One Across \citep{oneacross} provides all the same functionality as the
previous two solvers, along with a score. The score is linked to the number of 
people who have used the given answer (effectively it's a ratings system). One 
Across uniquely highlights how it has managed to deduce the answer, showing 
the break downs of each sentence. As with Cryptic Solver, One Across is a free 
service that doesn't require a subscription.


%%%
%% Problem Analysis :: Research Areas :: Natural Language Processing
%%%
\subsection{Natural Language Processing}

In order to correctly solve a clue, some form of natural language processing 
may be required. It is the natural language processing that could try to deduce 
the meaning of a clue. It is the meaning that can then be aligned with possible 
answers.

An example of natural language processing can be found within the One Across 
application. Given a clue (and a pattern) it will try to provide an accurate 
solution:

\begin{quote}
Spin broken shingle (7) =\textgreater  ENGLISH
\end{quote}

In order for the answer to be obtained, One Across will follow a natural 
language processing path and will provide it's trace path. The trace path shows
how the clue has been broken down to get to the answer. The trace path for the 
above clue can be found below:

\begin{quote}
`spin' is the definition.

`broken' means to anagram `shingle' to get ENGLISH.

ENGLISH matches `spin' with confidence score 100\%.
\end{quote}


%%%
%% Problem Analysis :: Research Areas :: Application Form
%%%
\subsection{Application Platform}

The existing products that have been discussed within this problem analysis 
have all been accessible via a browser. Although this is an acceptable 
platform, there could be a better platform that allows users to utilise the 
technology easier.

As previously mentioned, most crosswords are designed for users who have a few 
minutes to spare on the move. With the recent trends in owning a smartphone or 
tablet, there may be a gap in the market for a high quality mobile cryptic 
crossword solver.

Additionally it may also be the case that the system will need to be distributed
across several machines. The main reason for this could be the fact that the
system is too complex for it to be able to run efficiently upon a mobile device.
It is with this in mind that a review in to the various system architectures will need to be conducted along side the application format.

An in-depth review of all possible approaches will need to be conducted in order
to deduce the viability of this proposal.
