%%%
%% Development :: Resources
%%%
\section{Resources}
\label{sec:resources}

There are a number of resources which were needed to aid with solving 
the various clue types. As a lot of the solvers shared most of the resources 
a design decision was made to keep the resources in their own package for 
all solvers to access them as and when they need to.


%%%%
%% Development :: Resources :: Abbreviations
%%%
\subsection{Abbreviations}

Some clue types, for example the `Charade' clue type, require the knowledge 
of the different abbreviations that come with certain words. To provide this 
knowledge a file was found with a list of words and abbreviations in JSON 
format (JavaScript Object Notation). 

Listing \ref{abbr} illustrates the way in which the abbreviations for `quiet' 
are displayed in the file:

\begin{lstlisting}[caption={A sample of the abbreviations file},
                   label=abbr]  
 "quiet": [
  "p", 
  "pp", 
  "sh", 
  "mum"
 ], 
\end{lstlisting}

The Abbreviations class reads in all the possible abbreivations from the file 
at run time and stores them within a map which includes the word to get the 
abbreviations for and it's abbreviations as a set. 

There are two ways in which abbreviations could be needed to solve a clue, 
one way is to retrieve abbreivations for one word and the other is to 
retrieve abbreviations for a phrase or a whole clue. 

The method to retrieve abbreviations for one single word simply returns the 
set of abbreviations for a given word (or key) in the map if it exists within the 
file. 

The method to get abbreviations for a phrase or a whole clue gets the
abbreviations for as many words as possible in the given clue. For example,
``help the medic'' will contain seven abbreviations for the word  medic. ``medal
for the medic'' will contain four abbreviations for medal and seven  for medic.
However, the clue ``master of ceremonies'' will return one  abbreviation which
matches the entire clue (i.e. ``master of ceremonies'').  The algorithm is
greedy, and will attempt to match the biggest String possible in the given clue.
This means it will match all of the String  ``master of ceremonies'' before
matching abbreviations for ``master''.

%%%%
%% Development :: Resources :: Dictionary
%%%
\subsection{Dictionary}

The dictionary is an essential resource for the solving of clues to 
programmatically determine whether a string of letters is a valid word. 
A text file was found with a list of words within it which is read into the 
Dictionary class when an instance is created.

Listing \ref{dict} illustrates simply how the words in the dictionary file are
displayed:

\begin{lstlisting}[caption={A sample of the dictionary file},
                   label=dict]  
abaci
aback
abacs
abactinal
abactinally
abactor
abactors
abacus
\end{lstlisting}

Once the file has been read in, there are a custom list of words to  exclude
from the dictionary and a list of words that need to be added  found from
solving particular clues.

One of the methods used regularly is the filtering method which removes any
words from a given collection that are not present in the dictionary. This is an
effective way to remove words that have being constructed by a solver algorithm
which are essentially just an assortment of letters which hold no identified
meaning.  A similar method is used to filter any prefixes passed in within a
collection that are  also not held in the dictionary.

When potential solutions have been found by a solver, it is necessary to ensure
the algorithm has returned solutions that fit the end solutions pattern.
Requirements  such as the length input by the user and any known letters input
by the user must  be adhered to. In the dictionary class there is a method which
gets all word matches  within the dictionary for a given solution pattern. As
with filtering solutions, there is  also a method to match up all words in the
dictionary that have the same prefix as  a prefix passed in.

There are also simple methods solvers can used to identify whether a single word
or a  phrase is contained within the dictionary simply by checking whether the
collection the  dictionary file has been read into contains the word or not.

%%%%
%% Development :: Resources :: Thesaurus
%%%
\subsection{Thesaurus}

For clue types which do not have the answer itself nested within it, it is
usually necessary  to take the clue words and find synonyms for them. This is
where the necessity for a thesaurus  applies to aid the algorithms in solving
clues. A thesaurus file was found which holds a vast number  of entries where
each word after the first word in an entry is a synonym of the first word.

Listing \ref{thes} illustrates how the words in the thesaurus file are displayed
with the example word `dank':

\begin{lstlisting}[caption={A sample of the thesaurus file for the word `dank'},
                   label=thes]  
dank,boggy,damp,dampish,dewy,fenny,humid,marshy,moist,muggy,
     rainy,roric,roriferous,sticky,swampy,tacky,undried,wet,
     wettish
\end{lstlisting}

As with the other resources the file is read in and stored within a collection,
this  time in the form of a map where the first word is stored within an entry
along with it's synonyms.

There are a wide range of different methods that can be used to retrieve a
different array  of synonyms from vague to specific. Below is a list of
functionality that has been written  to retrieve synoynms:

\begin{itemize}
  \item Obtain a list of ``synonyms of a word's synonyms'' to increase the 
        chances of finding the correct solution. These must match against a 
        supplied pattern. 
  \item Obtain a list of ``synonyms of a word's synonyms'' to increase the 
        chances of finding the correct solution. These must match a minimum and
        maximum length passed in for the synonym.
  \item Retrieve all single word synonyms of a given word with a maximum and 
        minimum length (because some synonyms can be more than one word long) 
  \item Retrieve all synonyms of a given word with no pattern or minimum or 
        maximum length
  \item Get the synonyms for as many words as possible in the given clue. For 
        example, in the clue ``help the medic'', look for synonyms of ``help the
        medic'', ``help the'', ``the medic'', ``help'', ``the'', ``medic''.
  \item Retrieve all synonyms in the same entry in the thesaurus as a given 
        word. This means to not only look at the first word of an entry for 
        synonyms, look through all entries and return every entry which contains
        a given word.
  \item Retrieve all synonyms in the same entry in the thesaurus as a given word
        which match against the given pattern.
  \item Check if a given potential solution found by a solver matches as a 
        synonym against any of the words present in the clue.
\end{itemize}


%%%%
%% Development :: Resources :: Homonym Dictionary
%%%
\subsection{Homonym Dictionary}

The `Homophone' clue type requires a resource for retrieving homonyms for words.
A file was found which lists words with a string representation of the words
pronunciation  and as with the other resources, the file is read in and stored
within a collection holding  the word and an list of the pronunciation split
into chunks. 

An additional collection  is formed which is essentially a reverse of the first
collection created. This allows pronunciations  to be looked up faster. For
example, looking up the pronunciation ``HH AH0 L OW1'' will return  ``hello''.
This saves having to iterate the entire homophone map to search for words with
the same pronunciation.

Listing \ref{homonym} illustrates how the words in the homonym dictionary file 
are displayed with the example word `hello':

\begin{lstlisting}[caption={A sample of the homonym dictionary file for the word
                            `hello'}, label=homonym]  
HELLO  HH AH0 L OW1
\end{lstlisting}

The class allows the algorithm to retrieve the pronunciation of a given word as
well as  get words which share the same pronunciation as the supplied word. This
only works for words  which share the exact same pronunciation.


%%%%
%% Development :: Resources :: Categoriser
%%%
\subsection{Categoriser}

Some algorithms for certain clue types require indicators to determine how to
generate  the end solution. For example, the `Container' clue type requires an
indicator to identify  which word is the container word and which word is to be
contained. For the purpose of  providing a confidence score for an end solution,
indicators can also be used. As the clue  is passed to all solvers, it is
possible that two solvers may return the same answer back to the user.  By using
the indicator file associated with the clue type it is possible to assign a
higher rating  to a solution from a solver if the clue has an indicator within
it from the associated file.

To provide faster access to the indicators for each clue type, the files listing
the indicators  are read in and stored within a map in the Categoriser class
with the name of the clue type  and a collection of the indicators.

One use of the Categoriser class is to retrieve the indicators simply by passing
in a clue type.  Another, is the functionality to remove the indicator from a
clue to potentially speed up a solver  algorithm by removing extra unnecessary
checking on an indicator word.

Listing \ref{removing} illustrates how the indicator is removed from the clue:

\begin{lstlisting}[caption={Removing the indicator from the clue},
                   label=removing]  
 public String removeIndicatorWords(String c, String type) {
	// Remove any punctuation
	String clue = WordUtils.normaliseInput(c, false);
	// The indicator words for the given type have to be present
	if (indicators.containsKey(type)) {
		for (String i : indicators.get(type)) {
			if (clue.contains(i)) {
				// Only remove the first match
				clue = clue.replace(i, "");
				break;
			}
		}
	}
	// Remove any double spaces, etc...
	return WordUtils.normaliseInput(clue, false);
 }
\end{lstlisting}

The code above uses another class to remove any punctuation from the clue
itself, then it checks to see if the clue type has an entry within the map
storing all  the indicators. If a word in the clue matches an indicator in the
indicator file, it is  removed and the modified clue is returned.

As mentioned, the Categoriser class can also boost the confidence of a solution
if  it contains an indicator within the clue that is featured in the indicator
file.

Listing \ref{conf} illustrates how the confidence is boosted using indicators:

\begin{lstlisting}[caption={Boosting the confidence of a solution},
                   label=conf]  
 public void confidenceAdjust(Clue c, SolutionCollection solutions) {
	Collection<String> matchingTypes = getMatchingClueTypes(c);
	for (String clueType : matchingTypes) {
		for (Solution s : solutions) {
			if (clueType.equals(s.getSolverType())) {
				double confidence = Confidence.multiply(s.getConfidence(),
						Confidence.CATEGORY_MULTIPLIER);
				s.setConfidence(confidence);
				s.addToTrace("Confidence rating increased as the clue contains indicator
                      word(s) suggesting the solution is of type \"" + 
                      clueType + "\".");
			}
		}
	}
 }
\end{lstlisting}

The first line of code in the method above calls another method to retrieve  a
list of clue types that have an indicator in the associated indicator file which
matches a word  within the clue passed in. Then, all the solutions found from
all the solvers for the clue passed in  are matched against the clue types that
have been found and if the solver the solution has come  from matches a clue
type found, the confidence is boosted using a method in the Confidence class.
