\subsection{Performance}

The performance of the system should be good, however it must be noted that the
system is intended to run as a web service upon a server. The quality of the 
connection between the end user and the web service will be out of the scope of
this project.


\subsection{Legal and Access}

Within the project a number of data sources will be used. Firstly an English
dictionary will need to be accessed in order to allow the system to deduce if a 
given arrangement of characters formulates an English word.

In order to achieve this, an offline dictionary and an online dictionary will
need to be used. The offline dictionary is a short dictionary and is provided as
part of the GNU/Linux operating system under the GNU Licence Agreement. The 
online dictionary will be used to `fill in' any gaps in the short dictionary.
*** Offline Dictionary Licence to be added here ***

A number of cryptic crossword clues and solutions have been obtained from the
Guardian's website. The data will be used as a training set of data, when
testing the final software. The Guardian has given us permission to use their
data as long as the project remains within an academic environment, and that no
profit is made from the project.


\subsection{Backup and Recovery}

The project will make use of the git revision control system over a secure shell 
connection. The service provider is github, who offer a distributed setup to 
ensure that data is always available. Using a secure revision control system 
will ensure that:

\begin{enumerate}
  \item A copy of the project is stored upon a remote, secure server;
  \item Changes are able to be tracked;
  \item Issues and comments are able to be raised in a secure environment.
\end{enumerate}

The above measures will in effect be able to reduce against the loss, damage or 
theft of all project information.


\subsection{Archiving and Retention}

The University will retain a copy of the project (software product and the final
report) for assessment and evaluation purposes. 


\subsection{Maintainability}

The project -- including the software product -- will be maintained up until the
project hand in deadline: 18th April 2014.


\subsection{Availability}

The software will not contain any request or time limitations for users, and 
thus should be available at all times. However it must be stated that the server
availability that will be hosting the web service is out of the scope of the 
project.


\subsection{Capacity}

The end product should be able to handle a number of requests from different 
users at the same time. As the project is only intended as an academic project, 
large scale user support will be out of the scope of this project.
