\chapter{Software Specification} 
\label{chap:requirements} 

\citet{cadle10} states that there is a standard hierarchical approach in
structuring requirements. Table \ref{table:requirementsCategories} outlines the
main four categories:

\begin{table}[H]   
  \begin{tabular}{|l|l|l|l|}
  \hline     
  {\bf General}        & {\bf Technical}  & {\bf Functional} & {\bf Non-Functional}    \\ 
  \hline
  Business constraints & Hardware         & Data entry       & Performance             \\      
  Business policies    & Software         & Data maintenance & Security                \\      
  Legal                & Interoperability & Procedure        & Legal and Access        \\      
  Branding             & Internet         & Retrieval        & Backup and Recovery     \\      
  Cultural             & ~                & ~                & Archiving and Retention \\      
  Language             & ~                & ~                & Maintainability         \\      
  ~                    & ~                & ~                & Business Continuity     \\      
  ~                    & ~                & ~                & Availability            \\      
  ~                    & ~                & ~                & Usability               \\      
  ~                    & ~                & ~                & Capacity                \\     
  \hline   
  \end{tabular}
  \label{table:requirementsCategories} 
\end{table}


Although these are some of the sections usually found in the structure of
requirements there are several books which state that each section depends on
the type of project being undertaken. 

\citet{robertson13} mentions that `a requirement is something the product must 
do to support its owners business, or a quality it must have to make it 
acceptable and attractive to the owner.' The aim of gathering the requirements 
has always been to ensure that all ambiguities are removed before a product is 
developed. 

As well as the process of requirements engineering there are standards available
for organizations to adhere to when compiling their documents. A more common
standard is the ISO 9001 for Quality Assurance. In the document it is described
that an organizations system is influenced by:

\begin{itemize}
  \item its organizational environment, changes in that environment, and the 
        risks associated with that environment
  \item its varying needs
  \item its particular objectives
  \item the products it provides
  \item the processes it employs
  \item its size and organizational structure
\end{itemize}
\hfill\citep{iso08}

As the project consists of four members whom are part of all development teams 
such standards do not need to be followed but an awareness of these standards is
beneficial. The advantage of a standard such as the ISO 9001 would be to the
project would be only if the project is integrated as a business outside the
scope of University studies.

The following sections have been derived from the book by \citet{robertson13}.
The book contains a very useful template called the Volere template which aims
to recognize as much information required when engineering requirements.


% Project Drivers % Purpose 
%\newpage
%\input{requirements/project_drivers/purpose}

% Client, customer and stakeholder 
%\newpage
%\input{requirements/project_drivers/client_cust_and_stakeholder}

% Aims and Objectives
\newpage
\input{requirements/project_drivers/aims_and_objectives}

% Project Constraints % Mandated Constraints 
\newpage
\input{requirements/project_constraints/mandated_constraints}
% Relevant_Facts_And_Assumptions 
\input{requirements/project_constraints/relevant_facts_and_assumptions}


% Naming_Conventions And Terminology  
%\newpage
%\input{requirements/project_constraints/naming_conventions_and_terminology}

% Functional Requirements

% Scope
\newpage
\input{requirements/functional_requirements/scope}

% Business Data Model & Data Dictionary 
%\newpage 
%\input{requirements/functional_requirements/business_data_model_&_data_dictionary}

% The Scope of the Product 
%\newpage
%\input{requirements/functional_requirements/the_scope_of_the_product}

% Functional Requirements 
\newpage
\input{requirements/functional_requirements/functional_requirements}

% Non-functional Requirements 
\newpage
\input{requirements/non_functional_requirements/non_functional_requirements}

%Look and Feel Requirements 
%\newpage
%\input{requirements/non_functional_requirements/look_and_feel_requirements}

%Usability and Humanity Requirements 
%\newpage 
%\input{requirements/non_functional_requirements/usability_and_humanity_requirements}

%Performance Requirements 
%\newpage
%\input{requirements/non_functional_requirements/performance_requirements}

% Operational and Environmental Requirements 
%\newpage 
%\input{requirements/non_functional_requirements/operational_and_environmental_requirements}

%Maintainability and Support Requirements 
%\newpage 
%\input{requirements/non_functional_requirements/maintainability_and_support_requirements}

%Security Requirements 
%\newpage
%\input{requirements/non_functional_requirements/security_requirements}

%Cultural Requirements 
%\newpage
%\input{requirements/non_functional_requirements/cultural_requirements}

%Legal Requirements 
%\newpage
%\input{requirements/non_functional_requirements/legal_requirements}

%Project Issues 
%Open Issues 
%\newpage
%\input{requirements/project_issues/open_issues} 

%Off-the-Shelf Solutions
%\newpage 
%\input{requirements/project_issues/off_the_shelf_solutions}

%New Problems 
%\newpage 
%\input{requirements/project_issues/new_problems}

%Tasks 
%\newpage 
%\input{requirements/project_issues/tasks}

%Migration to the New Product 
%\newpage
%\input{requirements/project_issues/migration_to_the_new_product}

%Risks 
\newpage 
\input{requirements/project_issues/risk_assessment}

%Feasibility Study
\newpage
\input{requirements/feasibility_study/feasibility_study}

%Costs 
%\newpage 
%\input{requirements/project_issues/costs}

%User Documentation and Training 
%\newpage
%\input{requirements/project_issues/user_documentation_and_training}

%Waiting Room 
%\newpage 
%\input{requirements/project_issues/waiting_room}

%Ideas for Solutions 
%\newpage
%\input{requirements/project_issues/ideas_for_solutions}


