%%% 
%% Project Management :: Allocation of Work 
%%% 
\section{Allocation of Work}
\label{sec:allocation_of_work}

The allocation of work was primarily voluntary from members of the team. During the first term the tasks were delegated by all team members to each other clarifying on the different components that they would be working on in order to ensure there was no clash between each other. The dates for work to be competed was set by the team leader to ensure that the team was working on schedule. Tasks were delegated on a weekly basis at the group meetings. The minutes can be found in the appendix. 

The tasks in the first term mainly focused upon individuals to be issued the task and produce the work by the following week to be reviewed by the rest of the team members in the meetings. By the second term when development started the tasks were delegated to be worked in pairs. The architecture of the system was primarily developed by Stuart Leader and interfaces by Luke Hackett but in collaboration with the remainder of the team members. After the architecture of the system had been produced each team member selected a task such as a solver and attempted to write the algorithms. For the low level clues an individual was able to produce the algorithms but for the further solvers the team had to collaborate and work together.

Finally during the documentation and report writing most of the report was produced parallel to term one with the research. Returning to the report after development proved to beneficial as team members were once again able to select components which required to be done and produce the work. Each produced work has been throughly checked over my the other team members to ensure that anything that has been produced and written is true to the point where all members have agreed the work is correct. 