%%%
%% Project Management :: People Involved
%%%
\section{People Involved}
\label{sec:people_involved}

A number of project stakeholders have already been outlined with the initial
problem analysis. Within this section the stakeholders that are involved with
the project will be redefined upon a more formal basis.

The `group' will be actively referred to throughout the project, and therefore 
the group will be defined. The group will have four members throughout the 
project, and these members are:

\begin{itemize}
  \item Leanne Butcher
  \item Luke Hackett
  \item Stuart Leader
  \item Mohammad Rahman
\end{itemize}

The project group is based largely upon democratic discussions and decisions,
however to ensure that group deadlocks do not occur Mohammad has been selected 
as the group leader.

The group will be assigned a project supervisor directly from the University.
The project supervisor will help to deal with an technical and non-technical
queries, whilst also ensuring the group remains upon a general focus. The
project supervisor may also suggest features and improvements to work that the
group managed to produce. The group's project supervisor is Dr. Gary Allen.

A weekly meeting will take place between all group members and the project 
supervisor to discuss all aspects of the project. This includes (but is not 
limited to) project issues, software development issues, research findings, 
possible improvements and code reviews.

As the project is a formal assessment, the project assessor and moderator will 
be classified as indirect stakeholders within the project. Dr Sotirios Batsakis
and Dr Colin Venters have been assigned the roles of project assessor and 
project moderator respectfully. Both the project assessor and moderator will 
have a limited amount of contact time with the group, but will be present at 
formal presentations that are scheduled throughout the year.

The project formally does not have any clients associated with the work, however
Dr Hugh Osborne has offered to fill a client-like role within the project. Hugh
has a keen interest in cryptic crosswords and the problem area that the group
intends to sole. The role of the client for the group project will be to input
ideas and potential requirements which Hugh, as an experienced solver of cryptic
crosswords, would consider to be necessary.
